Sound and Automated Synthesis of Digital\\ Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-03-01 hscc2017/paper.tex
RE badge
cite ASPLOS 2006 paper

\renewcommand{\baselinestretch}{0.992}
\allowdisplaybreaks
\include{macros}

@@

\title{
Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous
Plants%
\thanks{Supported by EPSRC grant EP/J012564/1,
ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}}

@@

Modern implementations of embedded control systems have proliferated with
the availability of low-cost devices that can perform highly non-trivial
control tasks, with significant impact in numerous application areas such as
environmental control and robotics~\cite{astrom1997computer, Franklin15}. 
Correct control is non-trivial, however.  The problem is exacerbated by
artifacts specific to digital control, such as the effects of
finite-precision arithmetic, time discretization and quantization noise
introduced by A/D and D/A conversion.  Thus, programming expertise is a key
barrier to broad adoption of correct digital controllers, and requires
considerable knowledge outside of the expertise of many control engineers.

@@

By contrast, we leverage a very recent step-change in the automation and
scalability of \emph{program synthesis}.  Program synthesis engines use a
specification as the starting point, and subsequently generate a sequence of
candidate programs from a given template.  The candidate programs are
iteratively refined to eventually satisfy the specification.  Program
synthesizers implementing Counter-Example Guided Inductive Synthesis
(CEGIS)~\cite{sketch} are now able to generate programs for highly
non-trivial specifications with a very high degree of automation.  Modern
synthesis engines combine automated testing, genetic algorithms, and
SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a,
DBLP:conf/lpar/DavidKL15}.

@@

In order to synthesize closed-loop digital control systems, we use a program
synthesis engine.  Our program synthesizer implements Counter-Example Guided
Inductive Synthesis (CEGIS)~\cite{sketch}.  We start by presenting its
general architecture followed by describing the parts specific to
closed-loop control systems.  A high-level view of the synthesis process is
given in Figure~\ref{DSSynth_process}.  Steps $1$ to $3$ are performed by
the user and Steps~A to D are automatically performed by our tool for
Digital Systems Synthesis, named \tool.

@@

We have presented a method for synthesizing stable controllers and an
implementation in a tool called \tool.  The novelty in our approach is that
it is fully automated and algorithmically and numerically sound.  In
particular, \tool marks the first use of the CEGIS that handles plants with
uncertain models and FWL effects over the digital controller.  Implementing
this architecture requires transforming the traditional CEGIS refinement
loop into a two-stage engine: here, the first stage performs fast, but
potentially unsound fixed-point operations, whereas the second stage
restores soundness by validating the operations performed by the first stage
using interval arithmetic.  Our experimental results show that \tool is able
to synthesize stable controllers for most benchmarks within a reasonable
amount of time fully automatically.  Future work will be the extension of
this CEGIS-based approach to further classes of systems, including those
with state space.  We will also consider performance requirements while
synthesizing the digital controller.

>>>>

\renewcommand{\baselinestretch}{0.99}
\allowdisplaybreaks
\include{macros}

@@

\title{
Sound and Automated Synthesis of Digital\\
Stabilizing Controllers for Continuous Plants%
\thanks{Supported by EPSRC grant EP/J012564/1,
ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}}

@@

% RE badge
\begin{tikzpicture}[remember picture,overlay]
  \node[anchor=north east,inner sep=0pt] at ($(current page.south west)+(8.1in,10.6in)$) {
     \includegraphics[scale=0.3]{hscc-badge2}
  };
\end{tikzpicture}%
%
Modern implementations of embedded control systems have proliferated with
the availability of low-cost devices that can perform highly non-trivial
control tasks, with significant impact in numerous application areas such as
environmental control and robotics~\cite{astrom1997computer, Franklin15}. 
Correct control is non-trivial, however.  The problem is exacerbated by
artifacts specific to digital control, such as the effects of
finite-precision arithmetic, time discretization and quantization noise
introduced by A/D and D/A conversion.  Thus, programming expertise is a key
barrier to broad adoption of correct digital controllers, and requires
considerable knowledge outside of the expertise of many control engineers.

@@

By contrast, we leverage a very recent step-change in the automation and
scalability of \emph{program synthesis}.  Program synthesis engines use a
specification as the starting point, and subsequently generate a sequence of
candidate programs from a given template.  The candidate programs are
iteratively refined to eventually satisfy the specification.  Program
synthesizers implementing Counter-Example Guided Inductive Synthesis
(CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} are now able to generate
programs for highly non-trivial specifications with a very high degree of
automation.  Modern synthesis engines combine automated testing, genetic
algorithms, and SMT-based automated
reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}.

@@

In order to synthesize closed-loop digital control systems, we use a program
synthesis engine.  Our program synthesizer implements Counter-Example Guided
Inductive Synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}.  We
start by presenting its general architecture followed by describing the
parts specific to closed-loop control systems.  A high-level view of the
synthesis process is given in Figure~\ref{DSSynth_process}.  Steps $1$ to
$3$ are performed by the user and Steps~A to D are automatically performed
by our tool for Digital Systems Synthesis, named \tool.

@@

We have presented a method for synthesizing stable controllers, implemented
in a tool called \tool.  Our approach is it is fully automated and
algorithmically and numerically sound.  \tool marks the first use of the
CEGIS that handles plants with uncertain models and FWL effects over the
digital controller.  We transform the traditional CEGIS refinement loop into
a two-stage engine: here, the first stage performs fast, but potentially
unsound fixed-point operations, whereas the second stage restores soundness
by validating the operations performed by the first stage using interval
arithmetic.  Our experimental results show that \tool is able to synthesize
stable controllers for most benchmarks within a reasonable amount of time
fully automatically.  Future work will be the extension of this CEGIS-based
approach to further classes of systems, including those with state space. 
We will also consider performance requirements while synthesizing the
digital controller.
